Verifying Demonstrations

### 2019-02-19 paper/identity-limits.tex
Comments out perfectly decentralized, private birth certs

This makes the audit trail more complex.
It is also difficult to detect modifications to these records, since they are 
not public.

\subsubsection{Perfectly decentralized and private birth-certificates approach}

There are no audit records, the one who can create authentic birth certificates 
can perform Sybil \dots

>>>>

This makes the audit trail more complex, but it is still possible to follow the 
audit trail.
However, it is difficult to detect modifications to these records, since they 
are not public.

%\subsubsection{Perfectly decentralized and private birth-certificates approach}
%
%In perfectly decentralized system
%There are no audit records, the one who can create authentic birth certificates 
%can perform Sybil \dots

### 2019-02-19 paper/protocol.tex
Comments out perfectly decentralized, private birth certs

Several entities are involved in our protocol.
First, \iac{CA} is responsible for certifying a one-to-one mapping between a 
person's identity and a cryptographic key\footnote{%
  This can be done by any \emph{logically} centralized 
  authority~\cite{SybilAttack}.
  Although a decentralized authority, as in the case of a collective 
  authority~\cite{collective-signing} powered by 
  proof-of-personhood~\cite{proof-of-personhood}, would be desirable, we think 
  that this has scalability issues.
  See the detailed discussion in \cref{identity-limits}.
  We will also return to this topic in \cref{Discussion}.
}.
The \ac{CA} is only involved in the setup phase.
Second, a participant is an individual who wants to participate in a given 
protest.
A participant can assume three different roles:
\begin{enumerate}
\item The \emph{organizer} has written a manifesto for the protest and 
  disseminated it to others.
\item A \emph{protester} is attending the protest and asks witnesses to vouch 
  for his presence.
\item A \emph{witness} provides proofs to protesters which state that the 
  protester was indeed participating and such that the proofs are verifiable by 
  third parties.
\end{enumerate}
In general, there is one organizer and every participant can act alternatively 
as both protester and witness.

>>>>

Several entities are involved in our protocol.
First, \iac{CA} is responsible for certifying a one-to-one mapping between a 
person's identity and a cryptographic key\footnote{%
  This can be implemented using any \ac{CA} that prevents Sybil 
  attacks~\cite{SybilAttack} and ensures a one-to-one mapping between a person 
  and a cryptographic key.
  \Ie for each identity it issues one-and-only-one cryptographic key.
}.
The \ac{CA} is only involved in the setup phase.
Second, a participant is an individual who wants to participate in a given 
protest.
A participant can assume three different roles:
\begin{enumerate}
\item The \emph{organizer} has written a manifesto for the protest and 
  disseminated it to others.
\item A \emph{protester} is attending the protest and asks witnesses to vouch 
  for his presence.
\item A \emph{witness} provides proofs to protesters which state that the 
  protester was indeed participating and such that the proofs are verifiable by 
  third parties.
\end{enumerate}
In general, there is one organizer and every participant can act alternatively 
as both protester and witness.
